%-------------------------
% Resume in Latex
% Author: aditya

%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
 
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aditya Aryan} \\ \vspace{1pt}
    \small 7827565965 $|$ \href{adityaaryan531@gmail.com}{\underline{adityaaryan531@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/aditya-aryan-3aa235249/}{\underline{linkedin.com/in/aditya}} $|$
     \href{https://aditya3d-portfolio.vercel.app/}{\underline{My Portfolio}} $|$
    \href{https://github.com/Aytaditya}{\underline{github.com/aditya}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Chennai, India}
      {Bachelor of Technology, Electrical and Electronics Engineering}{July 2022 -- Present}
    \resumeSubheading
      {Ryan Internation school}{New Delhi, India}
      {High School}{ April 2007 --  May 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Intern}{March 2024 -- Present}
      {Zvia Tech, Chennai}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Part of the web Development team and develops websites for the company}
    \resumeItemListEnd
    
    \resumeSubheading
      {Web Development Intern}{Oct. 2023 -- Present}
      {Natt Labs}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Honing my skills to build dynamic and user-friendly web applications}
        \resumeItem{ worked as MERN stack developer}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Technical-Blockchain member}{Sep. 2023 -- Present}
      {Google Developer Student Club, VIT Chennai}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Technical Blockchain member of the club}
    \resumeItemListEnd

    \resumeSubheading
      {Web Development Intern}{July 2023 -- Oct. 2023}
      {Anakage Technologies Private Limited}{Karnataka, India}
      \resumeItemListStart
        \resumeItem{was front-end developer during internship}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Programming member}{June 2023 -- Present}
      {IoTHINC  Club , VIT Chennai}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Technical Programming member of the club}
      \resumeItemListEnd


      

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Krypt} $|$ \emph{Solidity, Web3, hardhat, Tailwind, React, Javascript, Metamask}}{Jun. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Krypt is a user-friendly platform that empowers you to seamlessly send Cryptocurrency between wallets.It leverages the robust security of Metamask, to ensure smooth and reliable experience .}
            \resumeItem{With Krypt you can: Connect your wallet, Send crypto with ease, Track transactions.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{GitForge} $|$ \emph{MongoDb Atlas, Express, React, NodeJs, Docker, Tailwind, Github API, Javascript }}{May 2024 -- Present}
          \resumeItemListStart
            \resumeItem{This Project is Github inspired Web application built using MERN, tailwind and Docker integration. It uses passport.js for Github-based user authentication.}
            \resumeItem{Additionaly, the app features a liking system and top repository exploration section.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Velocity Mart} $|$ \emph{React, Tailwind, Firebase, Daisy UI, Javascript}}{Mar. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{VelocityMart is a centralized platform that offers a user-friendly interface for students to browse, negotiate, and access a wide range of resources such as books, mattresses, electrical components, study materials, sports equipment, and lab manuals. It aims to promote sustainable resource sharing within the campus community.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Smart Lottery System} $|$ \emph{Solidity, React, Web3, CSS, Metamask, Ganache}}{October 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Project for a lottery system integrated with a user-friendly frontend. Leveraging blockchain technology, this smart contract ensures transparency and security in the lottery process.frontend interface simplifies participation, result checking, and prize management, enhancing the overall user experience.It features a robust backend powered by Solidity.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, C++, JavaScript, HTML, CSS, MongoDB, Pug, Solidity, Typescript, Astro, Scss} \\
     \textbf{Frameworks}{: NextJs, React, Node.js, Express, Bootstrap, Tailwind, Hardhat, ShadCN, Web3, Material-UI, Daisy-UI, Chakra-UI } \\
     \textbf{Developer Tools}{: Android Studio, Visual Studio Code, Pycharm, IntelliJ, Vercel, Netlify, Railway, Git, Postman, Thunder Client, Remix, Metamask, Core, Docker, Firebase} \\
     \textbf{Softwares}{: ModelSim, R Studio, Labview, LTspice}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
